### 2016-03-17 titlepage.tex
titlepage.tex: Work around font limitations

% Upper part of the page. The '~' is needed because \\
% only works if a paragraph has started.
\textsc{\LARGE The Association for Computational Heresy}\\[0.5cm]

@@

\textsc{\Large A Record of the Proceedings of}\\[0.5cm]
% Title
\HRule \\[0.4cm]
{ \Huge \sf SIGBOVIK 2016 \\[0.4cm] }

@@

The tenth annual intercalary robot dance party in celebration

of workshop on symposium about $2^6$th birthdays; in particular,

that of Harry Q. Bovik

@@

% Bottom of the page
{\Large Carnegie Mellon University\\[0.25cm]
Pittsburgh, PA\\[0.3cm]
April 1, 2016}

>>>>

% Upper part of the page. The '~' is needed because \\
% only works if a paragraph has started.
\textsc{\LARGE the association for computational heresy}\\[0.5cm]

@@

\textsc{\Large a record of the proceedings of}\\[0.5cm]
% Title
\HRule \\[0.4cm]
{ \Huge \sf SIGBOVIK 2016 \\[0.4cm] }

@@

the tenth annual intercalary robot dance party in celebration

of workshop on symposium about $2^6$th birthdays{\fontspec{Birbaslo.ttf} ;} in particular{\fontspec{Birbaslo.ttf} ,}

that of harry q{\fontspec{Birbaslo.ttf} .} bovik

@@

% Bottom of the page
{\Large carnegie mellon university\\[0.25cm]
pittsburgh{\fontspec{Birbaslo.ttf} ,} pa\\[0.3cm]
april $1${\fontspec{Birbaslo.ttf} ,} $2016$}
